A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-12-18 main.tex
Fixing figure caption typos

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/eta_beta_hat.png}
     \caption{Estimation accurate of LMM-lasso-Rakitsch and LMM-lasso-ggmix for $\bbeta$ and $\eta$ for varying $\eta$ levels and sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\xi = 0.8$.}
    \label{fig:eta_beta_mse}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width = \textwidth]{figures/eta_beta_hat.png}
     \caption{Estimation accuracy and computing time of LMM-lasso-Rakitsch and LMM-lasso-ggmix for $\bbeta$ and $\eta$ for varying $\eta$ levels and sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\xi = 0.8$.}
    \label{fig:eta_beta_mse}
\end{figure}

### 2020-12-18 supplement.tex
Adding BNPSD reference
Using endfloat for genetic epi submission, un-numbering supplement
Fixing figure caption typos

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Supplementary materials}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% EMPIRICAL KINSHIP
\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/empirical_kinship.png}
    \caption{Empirical data with three subpopulations ($n_1=417, n_2 = 134, n = 37$), RRM.}
    \label{fig:empirical}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figures/niter_perLambda_point.png}
    \caption{The number of iterations per $\lambda$ value for LMM-lasso-Rakitsch and LMM-lasso-ggmix across varying sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\eta = 0.8$, and $\xi = 0.8$, and dichotomous-discordant environmental effect structure. Note that 100 is the maximum number of iterations for both implementations of LMM-lasso, so that numerous incidences of 100 iterations may indicate lack of model convergence.}
    \label{fig:niter}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplementary materials}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% EMPIRICAL KINSHIP
\begin{figure}[H]
    \centering
    \includegraphics[scale = 1]{figures/empirical_kinship.png}
    \caption{Empirical data with three subpopulations, Caucasian ($n = 417$), African American ($n = 134$), and Hispanic ($n = 37$), RRM.}
    \label{fig:empirical}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figures/niter_perLambda_point.png}
    \caption{Number of iterations per $\lambda$ value for LMM-lasso-Rakitsch and LMM-lasso-ggmix across varying sample sizes with Independent Subpopulations data, coarse subpopulation structure, $\eta = 0.8$, and $\xi = 0.8$, and dichotomous-discordant environmental effect structure. Note that 100 is the maximum number of iterations for both implementations of LMM-lasso, so that numerous incidences of 100 iterations may indicate lack of model convergence.}
    \label{fig:niter}
\end{figure}
